---
title: "krakenR API interface"
author: "Austin Haffenden"
date: "`r Sys.Date()`"
output: github_document
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r libs, include = FALSE}
library(krakenR)

```


#Introduction

This package interfaces with the kraken API. Currently only for the the GET functions and not all are implemented. It is a work in progress. 

# Get asset information

Interogate the API for information on the existing assets. Output returned as a
list with two elements: error and result. The error element is empty if no error occured. The result element is empty if an error occured. Currently default
settings so returns information on all assets:  

* asset_name = asset name  
* altname = alternate name  
* aclass = asset class (e.g. currency)  
* decimals = scaling decimal places for record keeping  
* display_decimals = scaling decimals for output display  

```{r asset, eval=TRUE, include=TRUE}
ast_inf <- get_asset_info()

ast_inf$error

ast_inf$result[[1]]

```

# Get OHLC data

Get market history OHLC data for a specified asset pair. Time frame interval
is specifed in minutes: 1 (default), 5, 15, 30, 60, 240, 1440, 10080, 21600. 
Since can also be provided in Unix long form. Output returned as a list with 
two elements: error and result. The error element is empty if no error occured. The result element is empty if an error occured. Result contains two elements:
the returned OHLC data and the 'last' date in the data set. The default since 
is 0 (earliest). Data returned:  
time; open; high; low; close; vwap; volume; count

```{r OHLC}
ohlc <- get_ohlc_data(pair = "BCHEUR", interval = 30, since = 0)

ohlc$error

head(ohlc$result$BCHEUR)

ohlc$result$last
```

# Get order book

Return the current bid and ask orders for a specific asset. Output returned as
a list with two elements: error and result. The error element is empty if no 
error occured. The result element is empty if an error occured. Result contains
two elements: asks; bids. Optional to pass 'count', the maximum number of 
asks/bids (not implemented). Data returned as:  
price; volume; timestamp

```{r order}
ord <- get_order_book("BCHEUR")

ord$error

head(ord$result$BCHEUR$asks)

head(ord$result$BCHEUR$bids)

```
# Get recent spread data

Returns the recent spread data for a specified asset from a specified since.
Output returned as a list with two elements: error and result. The error 
element is empty if no error occured. The result element is empty if an error
occured. Result contains two elements: the spread entries for the asset; last,
the id to be used as since when polling for new spread data. Data returned as: 
time; bid; ask

```{r spread}
sprd <- get_recent_spread("BCHEUR", since = "1530876860")

sprd$error

head(sprd$result$BCHEUR)

sprd$result$last

```

# Get recent trades

Returns the recent trades for a specified asset from a specified since (default
is zero). Output returned as a list with two elements: error and result. The
error element is empty if no error occured. The result element is empty if an error occured. Result contains two elements: the trade data for the specified
asset over the specified period; last, the id to be used as since when polling for new trade data. Data returned as: 
price; volume; time; buy/sell; market/limit; miscellaneous

```{r trades}
trd <- get_recent_trades("BCHEUR", since = "1501605300157840478")

trd$error

head(trd$result$BCHEUR)

trd$result$last

```

# Get server time

Returns a unix timestamp and an RFC 1123 time format. This is to aid in 
approximating the skew time between server and client. 

```{r time}
get_server_time()

```

# Get ticker info

Returns the ticker info for a comma seperated list of assets. Output returned
as a list with two elements: error and result. The error element is empty if no error occured. The result element is empty if an error occured. Data returned
for each pair:  

* a = ask array(price, whole lot volume, lot volume)  
* b = bid array(price, whole lot volume, lot volume)  
* c = last trade closed array(price, lot volume)  
* v = volume array(today, last 24 hours)  
* p = volume weighted average price array(today, last 24 hours)  
* t = number of trades array(today, last 24 hours)  
* l = low array(today, last 24 hours)  
* h = high array(today, last 24 hours)  
* o = today's opening price  

```{r ticker}
pair_list <- paste("BCHEUR", "XBTEUR", sep = ",")
tick <- get_ticker_info(pair_list)

tick$error

tick$result$BCHEUR


```
# Get tradeable asset pair

Returns the requested information for a comma seperated list of tradeable asset
pairs. Information requested can be: "info": all info (default); "leverage":
leverage info; fees: fees schedule; margin: margin info.Output returned as a
list with two elements: error and result. The error element is empty if no 
error occured. The result element is empty if an error occured. 
Data returned is: 

* pair_name = pair name 
* altname = alternate pair name  
* aclass_base = asset class of base component  
* base = asset id of base component  
* aclass_quote = asset class of quote component  
* quote = asset id of quote component  
* lot = volume lot size  
* pair_decimals = scaling decimal places for pair  
* lot_decimals = scaling decimal places for volume  
* lot_multiplier = amount to multiply lot volume by to get currency volume  
* leverage_buy = array of leverage amounts available when buying  
* leverage_sell = array of leverage amounts available when selling  
* fees = fee schedule array in [volume, percent fee] tuples  
* fees_maker = maker fee schedule array in [volume, percent fee] tuples 
(if on maker/taker)  
* fee_volume_currency = volume discount currency  
* margin_call = margin call level  
* margin_stop = stop-out/liquidation margin level  

```{r tap}
tap <- get_tradable_asset_pair(info = "margin", 
                               pair_list = "BCHEUR, XBTEUR")

tap$error

tap$result$BCHEUR

```
